---
title: "Candy Data Analysis"
output: html_notebook
---
```{r}
library(tidyverse)
```

```{r}
all_candy <- read_csv("/Users/codeclanstudent/codeclan_projects/dirty_data_project_karolina/task4/clean_data/candy.csv")
```

1. The total number of candy ratings (not raters) given across the three years.

```{r}
all_candy %>%
  filter(!is.na(ranking)) %>% 
  summarise(total_ranking = n())
```
2. The average age of people who are going out trick or treating and the average age of people who are not going trick or treating.

```{r}
all_candy %>%
  drop_na(trick_or_treat) %>% 
  group_by(trick_or_treat) %>% 
  summarise(avg_age = mean(age, na.rm = T))
```

3. For each of joy, despair and meh, which candy bar revived the most of these ratings?

```{r}
candy %>% 
  drop_na(ranking) %>% 
  filter(ranking == "meh") %>% 
  group_by(candy_type) %>% 
  summarise(meh = n()) %>% 
  arrange(desc(meh)) %>% 
  head(1)

```
```{r}
candy %>% 
  drop_na(ranking) %>% 
  filter(ranking == "joy") %>% 
  group_by(candy_type) %>% 
  summarise(meh = n()) %>% 
  arrange(desc(meh)) %>% 
  head(2)
```
```{r}
candy %>% 
  drop_na(ranking) %>% 
  filter(ranking == "despair") %>% 
  group_by(candy_type) %>% 
  summarise(meh = n()) %>% 
  arrange(desc(meh)) %>% 
  head(1)
```

Alternative way

```{r}
candy %>%
  filter(!is.na(ranking)) %>%
  group_by(ranking, candy_type) %>%
  summarise(count = n()) %>%
  filter(count == max(count))
```


4. How many people rated Starburst as despair?

```{r}
all_candy %>% 
  filter(candy_type == "starburst" & ranking == "despair") %>% 
  summarise(count_starburst_despair = n())
```
5. Count despair as -1, joy as +1 and meh as 0

```{r}
num_in_ranking <- all_candy %>% 
  mutate(ranking = case_when(
    ranking == "joy" ~ 1,
    ranking == "despair" ~ -1,
    ranking == "meh" ~ 0,
    T ~ NA_real_
  ))
```

6. The most popular candy bars by above rating system for each gender in the dataset

```{r}
num_in_ranking %>% 
  filter(gender == "female") %>% 
  group_by(candy_type) %>% 
  summarise(score = sum(ranking, na.rm = T)) %>% 
  arrange(desc(score)) %>% 
  head(2)
```

```{r}
num_in_ranking %>% 
  filter(gender == "male") %>% 
  group_by(candy_type) %>% 
  summarise(score = sum(ranking, na.rm = T)) %>% 
  arrange(desc(score)) %>% 
  head(2)
```

Alternative way

```{r}
num_in_ranking %>%
  filter(!is.na(gender)) %>% 
  group_by(gender, candy_type) %>%
  summarise(avg_ranking = mean(ranking, na.rm = TRUE)) %>%
  filter(avg_ranking == max(avg_ranking))
```

7. The most popular candy bar in each year

```{r}
num_in_ranking %>% 
  filter(year == "2015") %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```

```{r}
num_in_ranking %>% 
  filter(year == "2016") %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```


```{r}
num_in_ranking %>% 
  filter(year == "2017") %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```

Alternative way

```{r}
num_in_ranking %>%
  group_by(year, candy_type) %>%
  summarise(avg_ranking = mean(ranking, na.rm = TRUE)) %>%
  filter(avg_ranking == max(avg_ranking))
```


8. The most popular candy bar by above rating for people in US, Canada, UK and all other countries

```{r}
num_in_ranking %>% 
  filter(country == "usa") %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```

```{r}
num_in_ranking %>% 
  filter(country == "uk") %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```

```{r}
num_in_ranking %>% 
  filter(country == "canada") %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```

```{r}
num_in_ranking %>% 
  filter(!country%in% c("canada", "usa", "uk")) %>% 
  group_by(candy_type) %>% 
  summarise(favorite = sum(ranking, na.rm = T)) %>% 
  arrange(desc(favorite)) %>% 
  head(2)
```

Alternative way

```{r}
num_in_ranking %>%
  mutate(country = if_else(country %in% c("united states", "canada", "united kingdom"), country, "other")) %>%
  group_by(country, candy_type) %>%
  summarise(avg_ranking = mean(ranking, na.rm = TRUE)) %>%
  filter(avg_ranking == max(avg_ranking))
```

